Climate Prediction Markets and the Convergence of Forecasting Models: An Agent-Based Simulation

### 2016-03-01 paper.Rmd
paper plot

---
title: "Climate Prediction Markets and the Convergence of Forecasting Models: An Agent-Based Simulation"
author: " "
date: "Feb 29, 2016"
output: 
  pdf_document:
    keep_tex: true
bibliography: library.bib
---

@@

Our sensitivity analysis, Fig X.

```{r, one, eval=TRUE, echo=FALSE, message=FALSE, htmlcap=tabRef("one", "dfd")}

@@

`r figRef("data_explore")`

```{r, data_explore, eval=TRUE, echo=FALSE, message=FALSE, htmlcap=figRef("data_explore", " "), fig.width=10, fig.height=5}

#multi_plot(p1, p2, cols = 2)
```

>>>>

---
title: "Climate Prediction Markets and the Convergence of Forecasting Models: An Agent-Based Simulation"
author: " "
date: "March 1, 2016"
output: 
  pdf_document:
    keep_tex: true
bibliography: library.bib
---

@@

Our sensitivity analysis, `r figRef("sa")`, shows that

```{r sa, eval=TRUE, echo=FALSE, message=FALSE, htmlcap=figRef("sa", "Sensitivty analysis"), fig.width=5, fig.height=5}
library(eat)
load("output/src_future.Rda")
plot(src_future, outcome_var = "Convergence") + theme_classic() 
#multi_plot(p1, p2, cols = 2)
```

```{r sa2, eval=TRUE, echo=FALSE, message=FALSE, htmlcap=tabRef("sa2", "")}

@@
